---
title: "Is there a difference in the usage patter of the Bike Share Toronto's Annual and Casual users? An analysis of how this service is used by Torontonians in the summer months"
author: 
  - Aamishi Avarsekar
thanks: "Code and data are available at: https://github.com/aamishi/TorontoCityBikesAnalysis"
date: today
date-format: long
format: pdf
number-sections: true
---

```{r}
#| include: false
#| warning: false
#| message: false

#install.packages("opendatatoronto")
#install.packages("knitr")
#install.packages("lubridate")
#install.packages("tidyverse")
#install.packages("janitor")
```


```{r}
#| include: false
#| warning: false
#| message: false

library(knitr)
library(janitor)
library(lubridate)
library(opendatatoronto)
library(tidyverse)
```

### Abstract

The city of Toronto continuously strives to improve its form of transportation to make the lives of its citizens easier. One such segment that has not gone unnoticed is Toronto’s Public Bike Sharing Services. With x number of bikes and y number of docks present throughout the city, this service has become widely used that is also evident from the introduction of EBIKES[]. The users of the Bike Share Toronto are mainly categorized into two groups: Annual and Casual users, based on their subscription plan. This paper aims to investigate who is more likely to use the service throughout the summer months of Toronto, and what stations and time periods are more likely to be used by each of the different types of users. 


## Section 1: Data

## Section 2: Results & Discussion

## Section 3: References























